SDR enhancement by clouds

### 2024-03-17 article/article.Rmd
Commit 2024-03-17 23:19

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/energy-2.png")
```

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/P_energy-2.pdf")
```

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/energy-1.png")
```

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-1.png")
```

>>>>

<!-- ```{r echo=FALSE, fig.cap="Trend of number of CE cases"} -->
<!-- knitr::include_graphics("../images/energy-2.png") -->
<!-- ``` -->

```{r echo=FALSE, fig.cap="Trend of number of CE cases"}
knitr::include_graphics("../images/P_energy-6.png")
```

<!-- ```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
<!-- knitr::include_graphics("../images/energy-1.png") -->
<!-- ``` -->

```{r echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-5.png")
```

```{r echo=FALSE, fig.cap="Trend of the yearly median over irradiance due to CE over irradiance"}
knitr::include_graphics("../images/P_energy-8.png")
```
